### 2008-12-18 talk/ecoop2009/benchmarks.tex
answer to a comment, insert another one, fix a typo

Despite being only a microbenchmarks, this result is very important as it proves
that our strategy of intermixing compile time and runtime can yield to better
performances than current techniques.  The result is even more impressive if
we consider dynamically typed languages as TLC are usually considered much
slower than the statically typed ones.

>>>>

Despite being only a microbenchmark, this result is very important as it proves
that our strategy of intermixing compile time and runtime can yield to better
performances than current techniques.  The result is even more impressive if
we consider dynamically typed languages as TLC are usually considered much
slower than the statically typed ones.
